This dissertation presents the formulation and simulation of a Rendezvous and Docking or Berthing mission performed by a robotic spacecraft equipped with a manipulator, with emphasis on coherent mission--step sequencing and on consistency among models, reference frames, and control laws throughout the operational profile.
In this work, a proportional--derivative (PD) control law was applied. The PD controller was implemented in the MATLAB/Simulink software environment using standard built--in blocks. The controller itself is a well--established method in control theory and was not developed in this study; the contribution lies in its implementation and application to the specific simulation scenario.
The long--distance phase is represented by a Hohmann transfer between coplanar circular orbits, used to establish initial conditions for the short--distance approach. 
In this phase, relative motion is described by the linearized Hill--Clohessy--Wiltshire equations and regulated by proportional--derivative control, while the pursuer's attitude is modeled by Euler's equation for a rigid body.
In the final approach, the dynamic model is switched to a coupled spacecraft--manipulator system derived from Lagrange's equations, and the PD control law acts to mitigate attitude disturbances induced by joint motion. The robotic manipulator is controlled using a reference obtained through inverse kinematics.
Performance is assessed through the final end--effector position error, consistency of joint rotation, actuation speed, and maintenance of the pursuer's attitude and relative translation with respect to the target. The results indicate that the proposed architecture enables stable phase transitions with state coherence, supporting the controlled approach and alignment required in the studied scenario. Disturbances associated with switching the dynamic models during the final approach are noticeable.
Study limitations include the use of linearized relative dynamics restricted to coplanar circular orbits and the absence of environmental perturbations, which limits direct generalization to more complex operational scenarios.